** whitespaces are compressed, comments are discarded
.
three
\par
% comment

paragraphs
    \par\par
    % comment
 separated by par.

   this     paragraph  has a 	    few 
 words,   including
 % comment
 a comment.


 % spaces at the end
 
.


** how to force two paragraphs
.
text  \par
~
\par
more text
.


** standard double-newline paragraph separation (with OSX and Windows EOL support)
.
firstparagraph

 second
paragraph
.


** \\ and \newline do not add spaces (they \unskip)
.
first line \\
 second line

first line \newline
 second line
.


!** \mbox: restricted horizontal mode and linebreaks and paragraphs
.
x\mbox{
one \gobbleO space,
two \gobbleO[] spaces,
two \gobbleO{} spaces,

no wh \\[4cm]ite \newline sp \\ ace,

one \\[4cm] space,
one \linebreak[4]space,
one \linebreak[4] space,

xx\par

{xx \\  x}}x

\mbox{ there
is

a


space at the beginning and two at the end } .
.


!** \unskip breaks out of groups, \ignorespaces does not
.
text {\unskip} text, text {\ignorespaces} text,
.


!** a space is added after macros that take arguments
.
% TODO: add a brsp after ] and }
one \gobbleO space,
two \gobbleO[] spaces,
two \gobbleO{} spaces,
two \echoOGO{} spaces,
two \echoO[] spaces.
.


!** space hack to prevent multiple spaces
.
x \pagebreak x \nopagebreak x \vspace{1mm} x \label{hi} x \marginpar{test} x \index{something} x \glossary{word} x \nocite x \enlargethispage x
.


** more than two newlines, including spaces, equal two newlines
.
first paragraph

   
  


second paragraph
.


** comments are disregarded and won't add a paragraph
.
first paragraph


  % this should not cause another paragraph


second paragraph
.


** comments are disregarded and won't prevent a paragraph
.
first paragraph % this should not prevent the paragraph

second paragraph% this should not prevent the paragraph

third paragraph
.


** comments can remove a linebreak (i.e. space) and thus join lines
.
This is an % stupid
% Better: instructive <----
example: Supercal%
              ifragilist%
    icexpialidocious
.


** one space inside as well as after a group is kept, the rest is compressed or skipped
.
text with empty group {  } and more text

text with {a group} and more text

text with { a group } and more text

text with { a group  } and more text

text with {  a group  }  and more text
.


** macros without arguments ignore spaces afterwards
.
some \empty  text.
.


** force a space after a macro with {}
.
some \empty{} text.
.


** force a space after a macro with \
.
some \empty\ text.
.


** \ followed by tab or linebreak is also a space
.
some \empty\
text. And\	these
\
are spaces, but not\

this.
.


** escaped newlines in an empty document (or at the end of a document)
.
\


.


** escaped newlines at the start of a paragraph
.
\
x

.


** escaped newlines after an environment
.
\begin{center}
\end{center}
\

.


** spaces before and after horizontal environments
.
xx
\begin{empty}
  text\begin{empty}
    text
  \end{empty}
  \begin{empty}text
  \end{empty}
\end{empty}
xx
.
