** \bfseries declaration
.
Hello \bfseries is emphasized.
.


** \em and \emph{}
.
\em You can also \emph{emphasize} text.
.


s** \emph{} command and nesting
.
Hello, \emph{this} is emphasized.

\emph{emph \textup{normal}}, \textup{normal \emph{emph}}

\emph{emph \emph{normal}}

test {test \em\em\em test \em test}

\textit{You can also \emph{emphasize} text if it is set in italics}
.


** fonts stay until the surrounding group ends      TODO: same spans should be merged
.
outer { text \bfseries {what} more text } end outer
.


** fonts reach across paragraphs if no group ends
.
hello, \itshape what

are we going to do here?

\slshape
Wrap all the paragraphs.
.


** monospaced fonts do not use ligatures
.
\texttt{first test of -- and ---}
.


s** em lengths are relative to current font sizes
.
\small
a line of text\\[1em]
a line of text\\[1em]
% TODO: in LaTeX, \Huge changes ALL of the current paragraph! also above!
\Huge
a line of text\\[1em]
a line of text

\small
a line of text\\[1em]
a line of text

\Huge
a line of text\\[1em]
a line of text
.


s** lineheight and relative widths according to font size
.
This is yet another paragraph. With a lot of meaningless text and meaningless text meaningless text meaningless text.

\tiny This is yet another paragraph.  With a lot of meaningless\\[1em] text and meaningless text meaningless text meaningless text.

This is yet another \Large paragraph. With a lot of meaningless text and meaningless text meaningless text meaningless text.

This is yet another paragraph. With a\\[1em] lot of meaningless text and meaningless text meaningless text meaningless text.
.
